Tutorial for Runing Mouse Bone Marrow Dataset

### 2023-10-19 Demo_marrow_facs.Rmd

```{r}
knn = 10; major_vote = 5
A = Symmetric_KNN_graph(knn = knn, feature_space = feature_space)[[2]]
cell_block_loop = lapply(1:100,function(loop){
  GMM_subsampling(seed = loop, gene_partition, expr_dat = dat, cell_kNN_graph = A, major_vote)
})
cell_block_prop = Reduce(`+`, cell_block_loop) / length(cell_block_loop)
cell_block = cell_block_prop
```

@@

# Calculate Jaccard index between module activity & cell type
jaccard_index <- apply(cell_block, 2, function(module_col) {
  apply(one_hot_matrix, 2, function(one_hot_col) {
    1 - philentropy::distance(rbind(module_col,one_hot_col), method = "jaccard", mute.message=TRUE)
  })
})
```

@@

```{r}
pheatmap(jaccard_index[rev(ordered_cell_types),], 
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white")))(99))
```

@@

>>>>

```{r}
knn = 10; major_vote = 5
A = Symmetric_KNN_graph(knn = knn, feature_space = feature_space)$'adj_matrix'
cell_block_loop = lapply(1:100,function(loop){
  GMM_subsampling(seed = loop, gene_partition, expr_dat = dat, cell_kNN_graph = A, major_vote)
})
cell_block_prop = Reduce(`+`, cell_block_loop) / length(cell_block_loop)
cell_block = cell_block_prop
```

@@

# Calculate Jaccard index between module activity & cell type
jaccard_index <- apply(cell_block, 2, function(module_col) {
  apply(one_hot_matrix, 2, function(one_hot_col) {
    1 - philentropy::distance(rbind(module_col,one_hot_col), method = "jaccard", mute.message=TRUE)
  })
})
jaccard_index = jaccard_index[rev(ordered_cell_types),]
rm(ordered_cell_types)
```

@@

```{r}
pheatmap(jaccard_index,
         cluster_rows=FALSE, cluster_cols=FALSE, 
         scale = "none", 
         color = colorRampPalette(rev(c("firebrick3", "white")))(99))
```

@@

## Save Intermediate data
```{r}
save(gene_partition,dist,gene_hree,cell_block,jaccard_index,file = "./marrow_result/module_result.rdata")
```
